Enhancing \Hinf{} Norm Estimation using Local LPM/LRM Modeling: Applied to an AVIS\thanksref{thx}

### 2016-04-05 ch04-lrmhinf/lrmhinf.tex
Small stuff in CH04:

\begin{figure}
 \centering
  \setlength{\figurewidth}{0.45\columnwidth}
  \begin{subfigure}[b]{0.49\columnwidth}
    \input{\thisDir/figs/vibrationisolation-classical.tikz}
    \caption{Traditional set-up.}  
    \label{fig:lrmhinf:vibration-isolation:traditional}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\columnwidth}
    \input{\thisDir/figs/vibrationisolation-skyhook.tikz}
    \caption{Principle of sky-hook damping.}  
    \label{fig:lrmhinf:vibration-isolation:skyhook}
  \end{subfigure}
  \disclaimer{Figure based on \citep[Fig. 3 and 4]{Voorhoeve2015SYSID} and \citep[Fig. 3 and 6]{Karnopp1995}.}
  \caption{Conceptual illustration of (active) vibration isolation set-ups. In addition to the passive isolation (spring and damper), the active controller $C$ provides additional isolation using the measurement of the payload velocity ($y=v_z$).
  If the velocity relative to ground is measured (a), the controller design involves trading-off which disturbance should be suppressed better.
  When the absolute velocity the payload is measured (b), the controller can suppress both disturbances as it acts as a damper between a virtual fixed point (``sky'') and the payload.
  }
  \label{fig:lrmhinf:vibration-isolation}
\end{figure}

@@

On the other hand, when a measurement of the absolute velocity of the payload is available, the external disturbances can be reduced effectively.
Absolute velocity measurements can be obtained e.g. from inertial sensors~\citep{Collette2011} such as geophones~\citep{Rademakers2005MSc,Vandermaas2011MSc}.
In particular, such sensors suspend an inertial mass using suspension with very low resonance frequency to the payload.
By observing the relative movement of the inertial mass and the payload, the absolute velocity of the payload can be measured~\citep{Collette2011}.
Conceptually, the active controller $C$ can be seen as connected to an imaginary fixed point in the `sky' (\figref{fig:lrmhinf:vibration-isolation:skyhook}), which is not disturbed by $F_{\mathrm{d(ext)}}$ for an ideal sensor.
Consequently, the trade-off that exists in passive isolation is no longer relevant.
A compliant passive suspension can decouple the payload from external disturbances while the active controller acts as a stiff damper to the `sky' such that the effect $F_{\mathrm{d(pl)}}$ is suppressed.

>>>>

\begin{figure}
 \centering
  \setlength{\figurewidth}{0.45\columnwidth}
  \begin{subfigure}[b]{0.49\columnwidth}
    \input{\thisDir/figs/vibrationisolation-classical.tikz}
    \caption{Traditional set-up.}  
    \label{fig:lrmhinf:vibration-isolation:traditional}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\columnwidth}
    \input{\thisDir/figs/vibrationisolation-skyhook.tikz}
    \caption{Principle of sky-hook damping.}  
    \label{fig:lrmhinf:vibration-isolation:skyhook}
  \end{subfigure}
  \disclaimer{Figure based on \citep[Fig. 3 and 4]{Voorhoeve2015SYSID} and \citep[Fig. 3 and 6]{Karnopp1995}.}
  \caption{Conceptual illustration of (active) vibration isolation set-ups. In addition to the passive isolation (spring and damper), the active controller $C$ provides additional isolation using the measurement of the payload velocity ($y=v_z$).
  % If the velocity relative to ground is measured (a), the controller design involves trading-off which disturbance should be suppressed better.
  % When the absolute velocity the payload is measured (b), the controller can suppress both disturbances as it acts as a damper between a virtual fixed point (``sky'') and the payload.
  }
  \label{fig:lrmhinf:vibration-isolation}
\end{figure}

@@

On the other hand, when a measurement of the absolute velocity of the payload is available, the external disturbances can be reduced effectively.
Absolute velocity measurements can be obtained e.g. from inertial sensors~\citep{Collette2011} such as geophones~\citep{Rademakers2005MSc,vanderMaas2011MSc}.
In particular, such sensors suspend an inertial mass using suspension with very low resonance frequency to the payload.
By observing the relative movement of the inertial mass and the payload, the absolute velocity of the payload can be measured~\citep{Collette2011}.
Conceptually, the active controller $C$ can be seen as connected to an imaginary fixed point in the `sky' (\figref{fig:lrmhinf:vibration-isolation:skyhook}), which is not disturbed by $F_{\mathrm{d(ext)}}$ for an ideal sensor.
Consequently, the trade-off that exists in passive isolation is no longer relevant.
A compliant passive suspension can decouple the payload from external disturbances while the active controller acts as a stiff damper to the `sky' such that the effect $F_{\mathrm{d(pl)}}$ is suppressed.
